\documentclass[10pt,twocolumn]{article}

\usepackage[letterpaper,margin=0.85in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,calc,fit,backgrounds}
\usepackage[hidelinks]{hyperref}

% Sober systems-paper register. No color theming.
\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false
}

\newcommand{\carmix}{CARMIX}

\title{\carmix{}: An Operating System Organized Around \\
Content-Addressed Rematerialization of Live Execution\\[0.4em]
\large Interim / Preliminary Report, pending the full technical report}

\author{Loucas Louka}
\date{2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.92\columnwidth}{\centering
\small This is an interim, preliminary report. It states what is proven,
what is measured, and what is not yet built, so that it slots cleanly under a
later full technical report. Copyright 2026 Loucas Louka. Released with the
\carmix{} sources under the AGPL-3.0.}}
\end{center}

\begin{abstract}
\carmix{} is a research operating system kernel organized around a single
principle. A context switch, a page fault, a cross-machine migration, a
user and kernel crossing, a program load, and a process deschedule are treated
as one operation, the rematerialization of content-addressed state under a
freshly minted capability whose authority cannot exceed the source authority,
over BLAKE3 hashes. The contribution is this principle and its verified
demonstration, not feature completeness. The system boots on x86-64 through a
standard bootloader, runs a capability-guarded WebAssembly executor inside the
kernel, rematerializes computation state on one machine and across two machines,
persists a content-addressed object and a whole dematerialized process to disk
so they survive a genuine cold reboot, reclaims unreachable objects with a
durable reference-counted collector, partitions deduplication by authority domain
to close the cross-domain timing channel, brings up a second CPU as a multi-core
foundation, and ships a machine-checked Coq proof of its core authority
guarantee. The proof is axiom-free except for one stated collision-resistance
hypothesis. To keep the claims separable, every result is placed in one of three
maturity tiers. Tier 1 is built in \carmix{}, verified, and rdtsc-measured.
Tier 2 is proven theory not yet validated on \carmix{}. Tier 3 is a research
verdict or formal result whose implementation is not built. The Deterministically
Reproducible Consistent Cut result is Tier 2, and its validation gap has narrowed
now that the SMP foundation exists, but the multi-core consistent capture is not
yet demonstrated. The deduplication impossibility bound, the content-addressed
convergence verdict, and the userland phasing are Tier 3. Every runtime number
reported here was observed in the QEMU emulator and is quoted from the captured
serial transcript. \carmix{} is roughly forty to forty-five percent of the way to
a general-purpose operating system. It is a research prototype, not a finished
operating system, and the Limitations section states in full what is not built.
The honesty of that list, and of the tier labels, is what is meant to make the
proven parts credible.
\end{abstract}

\section{Introduction}

Operating system design has periodically been reorganized around a single
unifying abstraction. Unix made everything a file, so that a device, a pipe, and
a socket are reached through one descriptor interface~\cite{ritchie1974unix}.
Plan 9 carried that further and made everything a name in a per-process
namespace, so that resources on remote machines are mounted and used as local
names~\cite{pike1995plan9}. Each step took a heterogeneous set of operations and
expressed them through one interface, and the gain was conceptual economy, fewer
mechanisms to build, to reason about, and to secure.

\carmix{} proposes the next axis. Everything is a content-addressed object,
named by the BLAKE3 hash of its content, and the operations a kernel performs on
live execution state are unified as one operation over those objects:
rematerialization. To rematerialize a computation is to reconstruct it elsewhere
from its content address rather than to copy its bytes wholesale. A context
switch, a demand-paging fault, a migration to another machine, a syscall
crossing, a program load, and a deschedule then differ only in scope and in
where the destination state already resides. Each is a verified materialize-by-hash
under a re-minted capability whose authority is bounded by the source.

The synthesis is the contribution. Content-addressed migration of program state
exists in prior work, and capability systems exist in both hardware and software
forms. The new part is fusing them so that diff-proportional transfer and
monotonic capability re-mint emerge together from executing live state inside a
content-addressed immutable memory model, with the authority guarantee enforced
on every re-mint and tied to a machine-checked proof. This report states the
principle, walks the architecture subsystem by subsystem with each part tied to
the milestone that demonstrates it, states exactly what the Coq development
proves and its one assumption, and reports the measured numbers from the
emulator with honest framing of what each shows.

This report stratifies its claims by maturity, so that no result reads as more
finished than it is. \textbf{Tier 1} is built in \carmix{}, verified by its
self-tests, committed to the public repository at
\texttt{github.com/dlukel/CARMIX}, and rdtsc-measured in the emulator. The
Architecture and Evaluation sections are Tier 1 unless a sentence states
otherwise. \textbf{Tier 2} is proven theory that \carmix{} does not yet validate
in running code. \textbf{Tier 3} is a research verdict or formal result,
including clean impossibility and undecidability findings, whose implementation
is not built or is only partially started. The Tier 2 and Tier 3 results have
their own sections after the Evaluation, and each result is labeled with its tier
where it appears.

\section{The Principle}

Three pieces combine into one operation.

\textbf{Content-addressed state.} Every object in the computation's memory graph
is named by the BLAKE3 hash of its content, including the names of its children.
Identical content has one name and one stored copy. Changing an object yields a
new object with a new name, and the unchanged objects keep their names. There are
no paths, no keys, and no overwrite.

\textbf{Diff-proportional transfer.} Because a destination that holds an object
holds its name, a transfer sends only the objects whose names the destination
lacks. Unchanged sub-objects keep their names across an epoch and are never
resent, so the bytes on the wire track the size of the change, not the size of
the state. This is a property of the naming scheme, not a separate deduplication
pass.

\textbf{Monotonic capability re-mint.} A capability is a token of authority over
a region of memory with a permission set. \carmix{} never moves a live capability
across a boundary. It strips the capability to a plain position-independent
descriptor, transfers the content-addressed state, and mints a fresh local
capability at the destination through a re-mint gate. The gate is fail-closed.
The minted capability's bounds are no wider and its permissions no greater than
the source held. Over-authority is rejected, not silently clamped.

Stated operationally, when a computation's state is a graph of content-addressed
immutable objects, moving it to a destination that already holds part of that
graph moves only the objects the destination lacks, and the authority granted at
the destination is minted fresh under a gate that cannot exceed the source
authority. The first property is the structural diff. The second is the
anti-amplification re-mint. Figure~\ref{fig:funnel} shows the operations that
\carmix{} expresses through this one path.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
  node distance=2.2mm,
  op/.style={draw, rounded corners=2pt, font=\scriptsize, align=center,
             minimum width=20mm, minimum height=5mm},
  core/.style={draw, thick, rounded corners=3pt, font=\scriptsize\bfseries,
               align=center, minimum width=34mm, minimum height=9mm, fill=black!6},
  ar/.style={-{Latex[length=1.6mm]}, gray}
]
\node[op] (cs) {context switch};
\node[op, below=of cs] (pf) {page fault};
\node[op, below=of pf] (mig) {cross-machine\\migration};
\node[op, below=of mig] (uk) {user/kernel\\crossing};
\node[op, below=of uk] (ld) {program load};
\node[op, below=of ld] (ds) {process\\deschedule};

\node[core, right=18mm of mig, yshift=4mm] (core)
  {rematerialize\\content-addressed\\state under a\\re-minted ceiling};

\foreach \n in {cs,pf,mig,uk,ld,ds} \draw[ar] (\n.east) -- (core.west);

\node[op, right=12mm of core, fill=black!3] (out)
  {verified by\\BLAKE3 +\\anti-amp gate};
\draw[ar] (core.east) -- (out.west);
\end{tikzpicture}}
\caption{The one-operation funnel. Six kernel operations on live execution
state are expressed as one operation, rematerialization of content-addressed
state under a re-minted capability ceiling, with integrity by BLAKE3 and
authority by the anti-amplification gate.}
\label{fig:funnel}
\end{figure}

\section{Architecture}

This section walks the system from the proven modules up through the kernel, and
ties each subsystem to the milestone in which it was observed. Milestone codes
(for example E2, R3, C3, M4) match the kernel self-test stages and the captured
serial transcript. Everything in this section is Tier 1, built in \carmix{} and
observed in the captured transcript, with the measured costs reported in the
Evaluation.

\subsection{Proven modules}

Five modules below the kernel hold the model and ship byte-identical to their
verified form.

\textbf{Capability model (cap/).} A capability is a record of a base, a length, a
permission set, and a validity tag. \emph{Strip} turns a live capability and a
reference to its referent into a plain descriptor carrying offset, length,
permissions, and the content hash of the referent, with no live authority tag.
\emph{Re-mint} takes a destination root, a descriptor, and the destination's copy
of the referent, and mints a fresh capability, checking in order that the
descriptor is well formed, that its bounds fit the source region, that its
permissions are a subset of the source, that write and execute are not both
requested, and that no forbidden permission is present. Any failure returns an
invalid capability.

\textbf{Content-addressed object store (store/).} The store maps a BLAKE3 hash to
bytes. Putting bytes returns their hash and stores one copy. Putting identical
bytes again stores nothing new. The vendored BLAKE3 is validated against the
official known-answer vectors, and the kernel re-runs that known-answer check at
startup before it trusts any content-addressed result (milestone R0, digest of
the empty string matches \texttt{af1349b9..41f3262}).

\textbf{Single-level store and structural diff (sls/).} The single-level store
builds an object graph over the store. A leaf holds bytes. A node holds an ordered
list of child identities. Mutation produces a new object and a new epoch, and
unchanged sub-objects keep their identities. The structural diff takes two epoch
roots and returns the changed set, pruning any subtree whose hash is unchanged,
memoizing visited identity pairs, calling no hash function, and resolving only as
many objects as actually changed.

\textbf{WebAssembly safety gate (gate/).} The gate runs untrusted WebAssembly
under software fault isolation~\cite{wahbe1993sfi,haas2017wasm}. It validates a
WebAssembly subset, lowers it to a small typed intermediate representation, and
runs a linear-time checker that rejects any module that could escape its linear
memory or forge a capability. A static elision pass drops a runtime bounds check
only for an access it has proven in bounds, and the checker rejects the elided
opcodes in untrusted input so they cannot be injected.

\textbf{Software capability backend (carmix/).} The backend enforces the
capability model with no capability hardware. Its re-mint logic is the same
decision logic as cap/, ported to software records with integer comparisons and
no rounding. This backend is what the bootable kernel uses, and the binary
contains no capability instructions.

\subsection{Boot and in-kernel execution}

The kernel boots on x86-64 through the Limine boot protocol, which hands it long
mode, page tables, a memory map, and a linear framebuffer. Everything above the
entry point is written for \carmix{}. The boot milestones B0 through B5 confirm
serial output, long mode (\texttt{CS=0x28}, \texttt{EFER.LMA=1}), a physical frame
allocator with read-back, a $1280\times800\times32$ framebuffer proven by pixel
read-back, and a PIT timer. The gate and the software backend, linked into the
kernel, run a WebAssembly task and draw its result (E1, result $=51$), and the
anti-amplification property holds in the kernel with one control accept and six
attack classes each rejected by its intended check (E2, $6/6$). The store and the
single-level store, linked in, checkpoint a counter and rematerialize it
bit-identically (R3), and demonstrate the diff-proportional structural diff (R4,
a one-leaf change reports one changed object, a self-diff reports zero, a
three-leaf change reports three).

\subsection{Desktop}

A software compositor draws a background and windows back to front with a
save-under cursor, driven by polled PS/2 keyboard and mouse. Windows support
focus raise on click, drag by the titlebar, and resize by a corner grip, each
proven by framebuffer pixel read-back. In the headless self-test run these events
are scripted and labelled as such. Only the final shell stage takes live PS/2
input. The desktop draws \carmix{}'s own windows in software and does not run
third-party graphical applications.

\subsection{Two-machine migration and signed authorization}

Two emulator instances share memory through an ivshmem device used as a byte
channel. The migration is a destination-pull protocol: the source advertises its
epoch root, the destination walks the root top down and marks the hashes it
lacks, requests them, and verifies each block's BLAKE3 hash before installing it,
pruning any subtree it already holds. A block whose recomputed hash does not match
the requested hash is rejected fail-closed.

Hash verification proves integrity, not provenance. A signed authorization record
closes that gap. The record binds the migration to an epoch root, a computation
identifier, a destination identifier, an authority ceiling, a nonce, and an
expiry, and the source signs it with real Ed25519 (vendored
tweetnacl~\cite{bernstein2012nacl,bernstein2012ed25519}). Before it installs and
re-mints, the destination checks, each fail-closed with a distinct reason, that
the signature is valid under the expected source key, that the signed root equals
the root it pulled, that the destination and computation identifiers match, that
the nonce is unseen and unexpired, and finally that the re-mint is capped at the
authority ceiling through the anti-amplification gate. One legitimate migration is
accepted and seven adversaries are each rejected by their own reason (milestone
D2).

\subsection{Key lifecycle}

The destination holds a trust store of an authority public key, the current
source public key, a monotonic lifecycle epoch, and a permanent revoked set.
Authority-signed enrollment sets the first source key, rotation replaces it, and
revocation adds a key to the revoked set. A lifecycle record applies only if it
verifies under the authority key and its epoch strictly exceeds the stored epoch,
which rejects replay and downgrade. Each migration carries its signing key, which
must be the current source key and not revoked. Six lifecycle attacks are each
rejected by a distinct verdict (milestone KA). The destination's first authority
key is baked in. Its bootstrap is out of scope and stated as such.

\subsection{The task substrate}

The kernel creates tasks and switches between them with a real assembly context
switch that saves and restores callee-saved registers and the stack pointer. A
cooperative yield calls it directly, and the timer interrupt calls it too, so a
task that never yields is still preempted (milestones P0 through P2). The
scheduling policy is isolated in one function, \texttt{pick\_next}, which is
round-robin and is a deliberate placeholder.

\subsection{The unified content-addressed task substrate}

On top of the substrate a task is made a content-addressed object. Its registers
and the used part of its stack hash into the proven store, the same state hashing
to the same handle and different state to a different handle (U0). Activate-by-hash
dematerializes the task to a hash and materializes it back, and the counter
survives the round trip (U1). Persistence falls out of this: a task dropped and
resumed from only its hash and the store resumes correctly, so the live and
durable forms are one object (U4). The cost is measured, not assumed. A raw
register switch is a flat cost near $1062$ cycles, while activate-by-hash costs
two to three orders of magnitude more at every dirty-set size, because hashing
dominates, with no dirty size at which it beats the register switch (U3). So the
fast switch stays the path for rapid preemption and content-addressing is used
only at coarse boundaries that already touch the store. The page-table root and
the capability slots are not yet part of the task state object.

\subsection{The residency manager}

Physical memory is managed as a content-addressed cache over the store. Fresh
allocation and mapping stay conventional. Fault-in and sharing collapse into
rematerialization. Free, eviction, and defragmentation partially collapse.
\texttt{materialize(hash)} fills a frame and verifies that its BLAKE3 equals the
requested hash, so integrity holds by construction (M2), a request for a resident
hash shares the existing frame and bumps its refcount, eviction writes a dirty
victim back before reuse with temporal victim selection (M3), and the hardware
page-table dirty bit is measured against the software chunk diff: both find the
same dirty set $\{1,4,6\}$ of eight pages and the hardware scan is roughly nine
times cheaper ($420{,}310$ against $3{,}956{,}943$ cycles, M4). Fixed chunks trade
external fragmentation for internal slack near $29$ percent on the measured mix,
and a frame-sized request stays serviceable (M5).

\subsection{The rematerializing fault handler}

Figure~\ref{fig:fault} shows the residency and fault path: a not-present access is
serviced as a verified materialize-by-hash, and a verification failure or a
protection fault is refused at the fault boundary.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
  box/.style={draw, rounded corners=2pt, font=\scriptsize, align=center,
              minimum height=6mm, minimum width=17mm},
  dec/.style={draw, diamond, aspect=2.2, font=\scriptsize, align=center, inner sep=0.5pt},
  bad/.style={draw, font=\scriptsize, align=center, minimum height=6mm,
              minimum width=17mm, fill=black!12},
  ar/.style={-{Latex[length=1.4mm]}}
]
\node[box] (acc) {access};
\node[dec, right=7mm of acc] (np) {not\\present?};
\node[bad, below=7mm of np] (prot) {protection\\fault: refuse};
\node[box, right=7mm of np] (res) {resolve addr\\$\to$ hash};
\node[box, right=7mm of res] (mat) {materialize\\from store};
\node[dec, below=7mm of mat] (vf) {BLAKE3\\matches?};
\node[bad, left=7mm of vf] (fc) {fail closed:\\no map};
\node[box, right=7mm of vf, fill=black!6] (mp) {map + resume\\(share if\\hash resident)};

\draw[ar] (acc) -- (np);
\draw[ar] (np) -- node[above,font=\tiny]{y} (res);
\draw[ar] (np) -- node[right,font=\tiny]{n} (prot);
\draw[ar] (res) -- (mat);
\draw[ar] (mat) -- (vf);
\draw[ar] (vf) -- node[above,font=\tiny]{n} (fc);
\draw[ar] (vf) -- node[above,font=\tiny]{y} (mp);
\end{tikzpicture}}
\caption{The residency and fault path (F1, F2, F3). A miss is a verified
materialize-by-hash. A protection fault and a verification failure are each
refused at the fault boundary, and an already-resident hash is shared.}
\label{fig:fault}
\end{figure}

Demand paging is automatic. A not-present access traps through the page-fault
vector, the handler classifies the fault (a protection fault is not a miss),
resolves the faulting address to a content hash, materializes the object with
BLAKE3 verification, installs the mapping, and returns so the faulting instruction
re-executes (milestone F1, a live page fault). If the loaded bytes do not hash to
the expected hash, the handler installs no mapping and does not resume (F2). Two
addresses bound to one hash share one resident frame, so deduplication happens on
the fault path (F3). Two address-to-hash bindings were measured head to head and
the choice does not move fault-service latency, because the cost is dominated by
the materialize and the hash (F4, a null finding). The handler's own memory is
resident so servicing a miss does not itself fault. A fault during fault handling
fails closed rather than recovering, and making it recoverable needs a separate
interrupt stack and a per-fault service context, named as future work (F5).

\subsection{Authority-bounded user and kernel crossing}

The kernel runs a process in ring 3 on its own page tables, with a task-state
segment, a trap gate, and the user and supervisor bit on the page tables. A
ring-3 access to a kernel address faults and is classified as a protection
violation, not a miss (US0). Entering the kernel is not ambient privilege: a
privileged crossing re-mints the caller's bounded authority for the requested
service through the same anti-amplification gate that bounds a migration and a
fault, so a confused deputy that hands the kernel a wider claim is held to the
re-minted authority (US2). Six userspace amplification attempts, an unheld
capability, an over-ceiling request, a forged epoch, a confused deputy, a
write-execute violation, and a forbidden permission, are each refused by their own
distinct status code, the same codes the migration table uses, with a replay
refused and a legitimate crossing accepted (US3). A large syscall argument is
passed as a hash and rematerialized by hash with verification rather than copied,
which closes the copy-at-use class of time-of-check to time-of-use race, since a
mutated object is a different hash and fails verification. This relocates trust to
the address-to-hash binding and the store admission rather than eliminating it
(US4).

\subsection{The process loader}

A program is a content-addressed object and loading a process is materialization.
A freestanding ring-3 ELF64 is stored, the loader parses its program headers, and
for each loadable segment it materializes the bytes by hash with BLAKE3
verification into a fresh ring-3 address space, with the segment's permissions and
no segment both writable and executable (L1, W$\oplus$X held). The process runs
under a capability re-minted through the gate at load time, so its authority is
bounded at birth and an over-ceiling or unauthorized request is refused by the
same gate (L3, each refused by a distinct reason). Loading the same image twice
gives two processes whose read-only code resolves to one physical frame by hash
while their writable data and stacks are private (L4, code refcount $=3$). The
image is embedded in the kernel because there is no filesystem yet.

\subsection{Concurrency}

The scheduler runs more than one ring-3 process at once, each with its own
page-table root, instruction and stack pointers, and re-minted ceiling, and the
timer preempts and restores exactly (C0). Each process is bounded by its own
ceiling and neither can exercise the other's authority (C1). A descheduled process
is dematerialized to a hash and its frames released, so not running and not
resident become different states, and on reselection the state is rematerialized
with verification and the process resumes, its counter surviving (C2). The cost is
measured: resuming a resident process is a register and page-table-root restore
near $13{,}958$ cycles, and resuming a dematerialized process is a store fetch, a
verification, and a remap near $1{,}029{,}941$ cycles, about seventy times more on
this run, with the run-to-run variation expected under emulation (C3, see the
Evaluation). Today the register context and the private data page dematerialize
while the page-table root stays resident.

\subsection{The policy, fairness, and the heap}

A rematerialization-aware policy decides when to dematerialize. By default a
descheduled process is kept resident, since resuming it is far cheaper.
Dematerialization happens only under memory pressure when the process is predicted
to stay descheduled long enough to repay the rematerialize cost, with a break-even
duration computed live from the measured resume cost rather than a guessed
constant, and an anti-thrash backoff that keeps a just-rematerialized process
resident (milestones PP0 through PP4). A fairness control sits on top: a process
repeatedly paying the rematerialize cost accumulates a measured per-process
progress deficit, and a bounded keep-resident bias removes the penalty source so
its progress rate recovers without starving its resident peer (FA0 through FA2).
The control bounds future unfairness and recovers the rate. It does not refund the
penalty already paid and accounts for one peer rather than many, so it is a first
measured control on a lightly-researched dimension, not a proven-optimal
algorithm. A per-process heap grows through an authority-bounded extend-heap that
crosses the re-mint gate, backed demand-zero (PM0, PM1). An idle page can be
dematerialized to a hash and rematerialized on fault (PM2), two processes that
independently write the same bytes deduplicate to one frame by hash with
copy-on-write where copy-on-write structurally cannot, since there is no shared
ancestor (PM3), and a hot churning page is excluded from dematerialization because
re-hashing it on every attempt is the fine-granularity cost the residency
measurement showed (PM4).

\subsection{Durable content-addressed persistence}

The store is made durable on a virtio-blk disk, so a content-addressed object and
a whole dematerialized process survive a genuine cold reboot (milestones DUR S1
through S7, commit \texttt{faebbd6}). A minimal polled virtio-blk driver provides
stable-media block read, write, and flush (S1). Objects go to an append-only log,
never overwritten, each as a header block carrying the claimed length and claimed
BLAKE3 written before its payload block, so an ordered-prefix truncation leaves a
partial record whose claim is present but whose payload re-hashes to a mismatch
and is rejected (S2). The hash-to-location index is not itself persisted. It is
rebuilt on every boot purely by scanning the log and re-verifying each record,
which is the recovery floor and also the evidence that RAM started empty, since
the index can only come from disk (S3).

The disk is treated as untrusted media and re-verified on every load, and the
cold reboot is genuine, each boot a separate QEMU process on the same host disk
image with empty RAM. An object written and flushed, then revived after a cold
reboot, rematerializes by its BLAKE3 hash with the on-disk bytes re-hashed before
they are served (S5). The headline is the persisted process (S6). A process is
dematerialized to its page-table-inclusive canonical task hash, its object graph
and a root block are persisted with the authority ceiling inside the hashed
manifest, the machine is cold-rebooted, the store is revived from disk with every
object re-hashed on load, and the process is rematerialized with its authority
re-minted through the same anti-amplification gate at the persisted ceiling. The
address-space root re-derived from the disk-loaded state equals the persisted
root, so the page-table-inclusive state is intact, and a load that requests
authority wider than the persisted ceiling is refused by the gate with its
distinct amplification status. Because the ceiling lives inside the hashed
manifest, tampering it changes the task hash and is caught by re-verification.
Tampering is caught on both an in-kernel manifest flip and a host-side payload
flip between boots, each rejected on the recovery scan or the load with the bytes
never served (S7). The crash consistency here is recovery-logic consistency under
an ordered-prefix write-order model, exercised exhaustively and reported with that
scope in the Evaluation and the Limitations. The honest scope is a single durable
writer and objects up to one payload block.

\subsection{Durable garbage collection}

The durable log would otherwise grow without bound, so unreachable objects are
reclaimed by a durable reference-counted collector (milestones GC1 through GC7,
commit \texttt{40c99cd}). No cycle collector is needed, because the
content-addressed graph is acyclic by construction. An object's BLAKE3 is computed
over its content including its referents' hashes, so a referent's hash must exist
before its referrer's hash can be computed, and an object cannot name its own or
an ancestor's hash (GC2). This is the runtime face of the Coq \texttt{acyclic\_graph}
result. Reference counts are mutable metadata about immutable objects, so they
live outside the hashed content, recorded as durable count-delta records in the
same append-only log under the same ordered-prefix discipline, and on a genuine
cold reboot the counts are reconstructed exactly by replaying those records (GC1).
The root set is the union of durable roots, the persisted root block and object
index, and volatile roots held in live process state (GC3).

Reclamation is crash-consistent with the tombstone as the commit point (GC4). The
reference removal and its count decrement are recorded first, the tombstone is
written second, and the storage is freed last. Truncating the
decrement-then-tombstone sequence at every byte offset, the forbidden state of a
tombstone present while a durable reference still names the object never occurs,
so a durable tombstone implies the count reached zero and no durable root reaches
a tombstoned object. Because deduplication is already present, a dedup hit can
arrive in the window between zero-count detection and the tombstone commit. That
window resurrects the zombie object, restoring its count with the same storage
block intact rather than freeing and recreating it (GC5). End to end, dropping a
reference reclaims the unreachable subgraph while reachable objects stay intact
and load-verify, and re-allocation reuses the freed blocks so the high-water mark
does not climb (GC6). The crash-consistency scope is the same
ordered-prefix-in-QEMU scope as the persistence proof. Concurrent tracing against
a live multi-threaded mutator and any cross-core reclamation race are not
implemented and wait on the SMP work.

\subsection{Domain-partitioned deduplication}

Deduplication is scoped to an authority domain, so an observer in one domain
cannot probe, by store hit-or-miss timing, for content held by another domain
(milestones DS1 through DS6, commit \texttt{4dd97a5}). The reference-count table
key gains an authority-domain tag, extending the collector's table rather than
forking a parallel one. Identical content stored in two domains produces two
distinct physical objects with independent counts (DS1), and a store deduplicates
only against existing objects in its own domain, a same-domain re-store hitting
and a cross-domain store missing (DS2). The security result is the closed channel,
stated precisely. The cross-domain store-hit-or-miss timing channel is closed by
partitioning, measured in the Evaluation, where a cross-domain probe now costs
what a genuinely new store costs rather than the fast hit it cost under global
deduplication (DS3). The resurrection window is made domain-aware, so a zombie in
one domain is not resurrected by a same-content store in another (DS4), and
reclamation still works under the domain-tagged counts (DS6). This is not a
general zero-leakage result. The within-domain timing channel remains, and it is
acceptable because the observer is already in that domain. The cost is duplicate
storage for content shared across domains, measured (DS5). The precise claim is
cross-domain channel closure at a measured storage cost. The formal boundary this
responds to is a Tier 3 finding stated later.

\subsection{The versioned capability gate}

A single-CPU versioned (MVCC) capability slot gives an authority transition a
single atomic commit point, so a capture firing at any instant reads a committed
pre-state or post-state capability and never a torn one (milestones VG1 through
VG5, commit \texttt{faae1d6}). The slot is a version word plus two capability
buffers, the active buffer selected by the low bit of the version. A replacement
is written to the inactive buffer, and the commit is one naturally-aligned
eight-byte store to the version word, which x86-64 makes atomic (VG1). The
anti-amplification check is the existing gate, reused unchanged, so the committed
capability is exactly what the proven check produces and never wider, and a
request for wider bounds or an added permission is refused with its distinct
status while the active capability is left unchanged (VG2). Driven through
sixty-four surrender-and-replace operations with captures fired at many points
across each operation, including during the inactive-buffer write, every capture
read a complete well-formed capability and none was torn, while a naive
single-buffer slot captured mid-write reads a torn capability that matches neither
the pre-state nor the post-state (VG3). The in-flight authority transient that
previously needed a drain collapses to the commit bump. This is demonstrated on a
single CPU, where there are no remote cores and no stale TLBs. It does not
implement or validate the multi-core memory cut or the cross-core capture, which
wait on the SMP work and on the Tier 2 result below. Its overhead is reported in
the Evaluation as small and at or below the measurement noise of the re-mint it
wraps, not a speedup.

\subsection{SMP bring-up: the multi-core foundation}

A second CPU is brought up, giving \carmix{} a genuine multi-core foundation
(milestones SMP S1 through S4, commit \texttt{40c99cd}). The run is under QEMU
with multi-threaded TCG, so the two virtual CPUs execute on separate host threads
and are genuinely parallel. Limine performs the standard INIT-SIPI-SIPI and hands
each application processor to the kernel in long mode, and the second core reaches
kernel C code and announces its LAPIC id on serial, which is observable proof a
second core is executing (S1). Each CPU has its own per-CPU record and increments
only its own counter (S2). The Local APIC is initialized in xAPIC mode on each
core, and a real inter-processor interrupt is delivered and handled in both
directions with an end-of-interrupt acknowledgement, which is the primitive every
future cross-core operation will build on, including the TLB shootdown a
multi-core capture would need (S3). The cross-core sanity test runs the same work
on both cores concurrently. Under a spinlock the shared counter totals exactly its
expected value, so the lock holds across real cores, and without the lock the
counter loses updates, which can only happen under truly concurrent
read-modify-write and is therefore positive evidence of parallel execution (S4).

This is the foundation only. It is engineering, not a research result, and it does
not by itself validate the multi-core consistent capture or the Deterministically
Reproducible Consistent Cut. After the test the application processor parks and
the single-CPU path runs as before. What this foundation unlocks, and the gap that
remains, is the subject of the Tier 2 section.

\section{Trust Model and the Anti-Amplification Proof}

\subsection{Threat model}

The two-machine threat model covers tamper (a block corrupted in transit),
impersonation (a party that is not the legitimate source induces a
rematerialization), replay (an old signed migration presented again to force a
stale epoch), and scope escalation (state for a different computation,
destination, or higher ceiling). The signing key itself is a target, with unknown
key, rotation forgery, rotation replay or downgrade, use after revoke, and
revocation forgery. Hash verification closes tamper. The signed authorization
record closes impersonation and scope, and the key lifecycle closes the key
attacks, each fail-closed with a distinct reason as Section~3 and the Evaluation
report. Figure~\ref{fig:trust} shows the layered checks.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  layer/.style={draw, rounded corners=2pt, font=\scriptsize, align=center,
                minimum width=62mm, minimum height=6mm},
  node distance=2mm
]
\node[layer, fill=black!2] (l1) {1. Ed25519 signature under expected source key\\(closes impersonation)};
\node[layer, below=of l1, fill=black!4] (l2) {2. signed root = pulled root\\(binds authorization to installed state)};
\node[layer, below=of l2, fill=black!6] (l3) {3. destination + computation identifiers match\\(closes wrong-scope escalation)};
\node[layer, below=of l3, fill=black!8] (l4) {4. nonce unseen, record unexpired\\(closes replay)};
\node[layer, below=of l4, fill=black!10] (l5) {5. re-mint capped at ceiling through the\\anti-amplification gate (closes authority escalation)};
\node[layer, below=of l5, fill=black!14, thick] (l6) {BLAKE3 hash verification of every block\\(integrity backstop, closes tamper)};
\end{tikzpicture}
\caption{The trust-model layers at the migration boundary. Each check is
fail-closed with a distinct reason, applied before any state is installed or any
capability is re-minted. The key-lifecycle current-key and not-revoked checks run
ahead of layer~1.}
\label{fig:trust}
\end{figure}

\subsection{The anti-amplification property}

The anti-amplification property is that a re-minted capability's base is no lower
and its limit no higher than the source region, and its permissions are a subset
of the source permissions. Figure~\ref{fig:gate} shows the gate. It is what makes
crossing, migrating, faulting, loading, and descheduling one authority model:
each goes through the same re-mint, and the gate is fail-closed, so over-authority
is rejected rather than clamped.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
  io/.style={draw, font=\scriptsize, align=center, minimum height=6mm, minimum width=20mm},
  chk/.style={draw, diamond, aspect=2.4, font=\scriptsize, align=center, inner sep=0.5pt},
  res/.style={draw, font=\scriptsize, align=center, minimum height=6mm, minimum width=16mm},
  ar/.style={-{Latex[length=1.4mm]}}
]
\node[io] (src) {source region\\+ requested\\bounds/perms};
\node[chk, right=8mm of src] (b) {bounds\\$\subseteq$ src?};
\node[chk, right=8mm of b] (p) {perms\\$\subseteq$ src?};
\node[chk, right=8mm of p] (wx) {no W$\land$X,\\no forbidden?};
\node[res, right=8mm of wx, fill=black!6] (ok) {valid cap\\$\sqsubseteq$ source};
\node[res, below=8mm of p, fill=black!12] (no) {invalid cap\\(rejected)};

\draw[ar] (src) -- (b);
\draw[ar] (b) -- node[above,font=\tiny]{y} (p);
\draw[ar] (p) -- node[above,font=\tiny]{y} (wx);
\draw[ar] (wx) -- node[above,font=\tiny]{y} (ok);
\draw[ar] (b) -- node[right,font=\tiny]{n} (no);
\draw[ar] (p) -- node[right,font=\tiny]{n} (no);
\draw[ar] (wx) |- node[right,font=\tiny]{n} (no);
\end{tikzpicture}}
\caption{The anti-amplification re-mint gate. Every authority crossing in
\carmix{}, migration, fault, user/kernel crossing, load, and deschedule, passes
through this one fail-closed gate.}
\label{fig:gate}
\end{figure}

\subsection{What the Coq development proves}

The proof in \texttt{proofs/Carmix.v} models a capability as a record of a base, a
limit, a finite permission set, and a validity flag, with a forbidden permission
subset. It defines an authority order in which one capability is below another
when its validity implies the other's, its range sits inside the other's, and its
permissions are a subset. It defines a re-mint function that clamps the requested
range to the source, intersects the requested permissions with the source, rejects
a request for write and execute together or for any forbidden permission, and sets
validity accordingly. Three results are machine-checked, labeled C1, C2, and C3.

\begin{itemize}
\item C1, \texttt{anti\_amplification}: for all sources and requests, if the
re-minted capability is valid then it is below the source in the authority order.
\item C2, \texttt{valid\_dest\_no\_wx} and \texttt{valid\_dest\_no\_forbidden}: a
valid re-minted capability does not hold write and execute together and holds no
forbidden permission.
\item C3, \texttt{acyclic\_graph}: the content-addressed object graph is acyclic.
\end{itemize}

C3 is what makes the durable reference-counted collector of the Architecture
sound. An acyclic graph cannot form a reference cycle, so refcounts reach zero
exactly when objects become unreachable and no cycle collector is needed.

The development is axiom-free except for one stated hypothesis. The acyclicity
result is scoped honestly: it does not derive acyclicity from hashing alone.
Objects are modeled as a finite inductive tree, a node carrying a payload and a
list of child objects, so a child is a strict subterm of its parent, a structural
size measure strictly decreases along the child relation, and acyclicity follows
from that well-founded order. The single hypothesis, that the identity function is
injective (collision resistance), is what connects the hash-graph back to that
finite tree. The size measure is a proven lemma, not an assumption. The
development contains no \texttt{Admitted}, no \texttt{admit}, and no
\texttt{Axiom}. \texttt{coqc} and \texttt{coqchk} both accept it, and an audit
reports the three authority results as closed under the global context and
\texttt{acyclic\_graph} as carrying only the collision-resistance hypothesis.

The proof is about the abstract capability algebra. It is not a proof that the C
implementation in \texttt{carmix/swcap.c} refines this model. The runtime
correspondence is demonstrated, not proven, by the kernel attack tables (E2, US3,
D2, KA), each of which runs the real software backend and observes each adversary
rejected by its intended check. A machine-checked refinement of the C code against
this model is future work.

\section{Evaluation}

All runtime numbers below were observed in the QEMU emulator and are quoted from
the captured serial transcript. Cycle counts are \texttt{rdtsc} differences taken
under TCG emulation, so they are noisy run to run. That variation is real and is
reported as such, and the point of each measurement is the order of magnitude and
the direction, not a precise constant.

\subsection{The cost crossover}

A raw register context switch is a flat cost near $1062$ cycles, independent of
dirty-set size (U3). Activate-by-hash, which serializes and hashes the task state,
is two to three orders of magnitude more at every swept dirty size, and there is
no dirty size at which it beats the register switch, because the BLAKE3 hash of
even one chunk already dwarfs the register swap. This is the load-bearing negative
result: a scheduling policy that content-addresses on every switch is not viable
on this hardware, so content-addressing is reserved for coarse, infrequent
boundaries that already touch the store. Table~\ref{tab:crossover} reports the
incremental-cost measurement (U2) that anchors it: re-storing only the dirty set
tracks the dirty set, with a one-chunk change far cheaper than a full re-store.

\begin{table}[t]
\centering
\caption{Incremental dematerialization tracks the dirty set (U2). A
$4096$-byte page in $16$ chunks, measured cycles are \texttt{rdtsc} under TCG.}
\label{tab:crossover}
\small
\begin{tabular}{lrrr}
\toprule
case & dirty chunks & bytes & cycles \\
\midrule
baseline (all dirty) & 16 & 4096 & 1{,}066{,}976 \\
small (1 chunk)      & 1  & 256  & 278{,}448 \\
large (all chunks)   & 16 & 4096 & 815{,}649 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Resume cost and the break-even}

The deschedule resume path was measured directly (C3). Resuming a resident
process, a register and page-table-root restore, cost $13{,}958$ cycles. Resuming
a dematerialized process, a store fetch, a BLAKE3 verification, a writeback, and a
remap, cost $1{,}029{,}941$ cycles, a ratio near $73\times$ on this run. The
architecture narrative describes this path as about fifty times more expensive.
The spread between that figure and the $73\times$ measured here is the run-to-run
emulation noise the transcript notes explicitly. This single measured cost anchors
the policy. The break-even deschedule duration, the point past which freeing a
frame for the deschedule duration outweighs paying the extra resume cost, is
computed live from it at $493{,}223$ cycles (PP3). Table~\ref{tab:breakeven}
reports the net outcome across deschedule durations: shorter than the break-even
nets a loss, longer nets a gain. The anti-thrash backoff bounded a forced thrash
workload to a single dematerialization across seven rounds, keeping the process
resident on the other six (PP4).

\begin{table}[t]
\centering
\caption{Net outcome of dematerializing across deschedule duration, anchored in
the measured C3 resume cost (PP3). Net is freed-frame value over the deschedule
minus extra resume cost. Break-even $D^\ast = 493{,}223$ cycles.}
\label{tab:breakeven}
\small
\begin{tabular}{rrrl}
\toprule
duration (cyc) & freed value & extra cost & verdict \\
\midrule
123{,}305   & 253{,}993   & 1{,}015{,}983 & loss \\
246{,}611   & 507{,}989   & 1{,}015{,}983 & loss \\
493{,}223   & 1{,}015{,}981 & 1{,}015{,}983 & loss \\
986{,}446   & 2{,}031{,}962 & 1{,}015{,}983 & gain \\
1{,}972{,}892 & 4{,}063{,}924 & 1{,}015{,}983 & gain \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The dirty-bit comparison}

The unified-substrate crossover left open whether a cheap coarse filter could
front the content-addressing. The residency manager answers it (M4). A workload
wrote pages $\{1,4,6\}$ of eight. The hardware page-table dirty-bit scan and the
software \texttt{memcmp} chunk diff agree on the dirty set, and the hardware scan
cost $420{,}310$ cycles against the software diff's $3{,}956{,}943$, roughly nine
times cheaper. The hardware bit is the cheap coarse filter and content-addressing
is the fine mechanism, and they compose.

\subsection{Two-machine migration}

Table~\ref{tab:migration} reports the bytes on the wire between two emulator
instances. The cold sync transferred the full graph, $1093$ objects in $44{,}505$
bytes. Three warm hops after small changes transferred $1176$, $1176$, and $2219$
bytes. The third hop changed two leaves and fetched more than the first, which
changed one, so the warm transfer tracks each hop's own change set rather than a
constant. No block was rejected on these clean runs. A corrupted or forged block
is rejected fail-closed by the BLAKE3 hash check.

\begin{table}[t]
\centering
\caption{Two-machine diff-proportional migration, bytes on the wire, measured
between two emulator instances (milestones B2, B4).}
\label{tab:migration}
\small
\begin{tabular}{lrrr}
\toprule
sync & blocks & bytes received & store objects \\
\midrule
cold  & 1093 & 44{,}505 & 1093 \\
warm hop 1 & 4 & 1176 & 1097 \\
warm hop 2 & 4 & 1176 & 1101 \\
warm hop 3 & 7 & 2219 & 1108 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The adversarial tables}

The anti-amplification gate was run against attack classes at each boundary, and
each adversary was rejected by its own intended check, with a control accept.
Table~\ref{tab:adv} summarizes the runtime tables. The in-kernel anti-amp run
rejected $6/6$ (E2). The user and kernel boundary rejected six amplifications by
six distinct status codes plus a replay, with a legitimate crossing accepted
(US3). The migration trust boundary accepted one legitimate migration and rejected
seven adversaries each by a distinct reason (D2). The key lifecycle accepted the
legitimate enroll, rotate, and revoke flow and rejected six lifecycle attacks each
by a distinct verdict (KA). The status codes are shared across the boundaries,
which is the evidence that it is one gate.

\begin{table}[t]
\centering
\caption{Runtime adversarial tables. Each boundary runs the real software backend
and observes each adversary rejected by its intended check, with a control accept.}
\label{tab:adv}
\small
\begin{tabular}{llr}
\toprule
boundary & milestone & accept / reject \\
\midrule
in-kernel anti-amp & E2  & 1 / 6 \\
user/kernel crossing & US3 & 1 / 6 (+ replay) \\
two-machine migration & D2 & 1 / 7 \\
key lifecycle & KA & legit flow / 6 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Sharing and dedup}

Sharing a hash at admission re-materialized zero bytes and cost $116{,}891$
cycles, far less than a real fault at $2{,}456{,}493$ cycles per fault that moved
$4096$ bytes, so deduplicating on the way in beats a post-hoc merge (M2). On the
fault path two addresses bound to one hash shared one frame with a single store
fetch (F3). Two processes that independently wrote the same heap page, with no
shared ancestor, deduplicated to one physical frame by hash, and a later write
split a private copy under copy-on-write (PM3). A hot churning page is excluded
from dematerialization. Over a burst of $64$ rewrites the exclusion avoided about
$26{,}689{,}536$ cycles of repeated hashing (PM4). The fairness measurement (FA0)
showed a process dematerialized every turn paying $12{,}191{,}796$ cycles of
rematerialize penalty over twelve equal turns that its resident peer did not pay,
and the keep-resident control stopped the deficit from climbing and recovered the
victim's progress rate (FA1, FA2).

\subsection{Durable persistence cost and the crash proof}

A per-object durable write plus flush on the virtio-blk path cost $3{,}561{,}112$
cycles (DUR S1). After a cold reboot, re-verifying and indexing six objects by
scanning the log cost $46{,}884{,}349$ cycles, and the index came purely from
disk (S3). A cold-reboot object round-trip, the lookup, read, re-hash, and
compare, cost $3{,}099{,}346$ cycles (S5). The crash proof read the durable
two-record log back into its exact byte image and ran the boot recovery parser at
every one of the $16{,}385$ byte offsets of the write, modelling an ordered-prefix
truncation at each point. At all offsets the invariant held with zero violations,
the recovered store holding either the complete object whose bytes hash to its
name or no such hash, and never a hash naming torn bytes. The rejection branch
fired at $8{,}896$ offsets, every offset where a record's claim was present but its
payload incomplete, and the same branch fires on a one-byte payload tamper. The
proof pass cost $609{,}903{,}419$ cycles (S4). The scope is recovery-logic crash
consistency under an ordered-prefix write-order model in QEMU. Real-hardware write
reordering, cache and barrier semantics, and sub-sector tearing are out of scope
and named in the Limitations.

\subsection{The versioned gate overhead}

The versioned gate was measured against the unversioned re-mint over
twenty-thousand-iteration averages (VG4). The unversioned gate operation, a
re-mint into a single slot, cost $868$ cycles, and the versioned operation, a
re-mint plus the inactive-buffer write plus the atomic commit, cost $780$ cycles
on this run, so the measured versioning delta was zero this run and about $+168$
cycles on an earlier run. The honest finding is that the added work, a four-field
buffer copy and a single word bump, is small relative to the re-mint and at or
below the measurement noise on this hardware. It is not a speedup. The commit
point alone, the version bump, cost $14$ cycles, near the rdtsc resolution floor,
and the per-slot memory cost is $32$ bytes for the second buffer and the version
word.

\subsection{Durable GC cost and bounded growth}

An in-RAM reference-count increment or decrement cost $731$ cycles and the
zero-count reclamation decision cost $40$ cycles (GC7). The crash-proof pass over
the $8{,}193$ truncation points of the decrement-then-tombstone sequence cost
about $124{,}490$ cycles with zero invariant violations (GC4). End to end,
dropping a reference reclaimed three unreachable objects and $12{,}288$ bytes
while the reachable object stayed intact, and re-allocating three objects reused
the freed blocks so the high-water mark held instead of climbing (GC6). The log
no longer grows without bound.

\subsection{Dedup domain-partitioning: the closed channel and its price}

The cross-domain timing channel and its cost were measured directly (DS3, DS5). A
genuinely new store, a miss, cost $1{,}275{,}657$ cycles including the object
write and flush, and a within-domain hit cost $2{,}245$ cycles. A cross-domain
probe, probing from one domain for content another domain holds, cost $42{,}873$
cycles under global deduplication, a fast hit that leaks the content's existence,
against $1{,}285{,}349$ cycles under domain-scoped deduplication, the same order
as a genuinely new store. The timing under scoping no longer distinguishes
exists-in-another-domain from does-not-exist-anywhere, so the cross-domain channel
is closed. The within-domain hit at $2{,}245$ cycles remains, the acceptable
residual. The price is duplicate storage. The same content across three domains
stored three physical objects where global deduplication would store one, a
measured duplicate-storage cost of $8{,}192$ bytes.

\subsection{SMP bring-up and the cross-core race}

AP startup latency, measured from writing the application processor's entry
address to the processor signalling it is up, was $599{,}023$ cycles (SMP S1). In
the cross-core test each core attempted one hundred thousand increments of a
shared counter. Under the spinlock the counter totalled exactly $200{,}000$, so
the lock holds across cores, and without the lock it reached only $112{,}245$ of
the $200{,}000$ attempted, losing $87{,}755$ updates, which is positive evidence
the two cores ran truly in parallel (S4). No inter-processor interrupt round-trip
latency is reported because it was not measured in isolation on this run. The
functional result, delivery and handling in both directions, is what is reported
(S3).

\subsection{What the evaluation shows}

The measured advantage is repeated migration or deschedule of a large state with a
small change, where the transfer or the incremental store tracks the change. The
crossover and the resume cost show that content-addressing is not free and must be
confined to coarse boundaries, which is why the fast register switch stays the
common path. The dirty-bit result shows the cheap hardware filter composes with
the fine content mechanism. The adversarial tables show the one gate holds at every
boundary. The persistence and GC numbers show the durable substrate is
crash-consistent under the named ordered-prefix model and bounded in growth, the
dedup numbers show the cross-domain timing channel closes at a measured storage
cost, the versioned gate adds overhead at or below the measurement noise, and the
SMP foundation runs two cores genuinely in parallel. None of this is a claim about
raw compute speed, cold-start migration, or operating-system completeness.

\section{Formal Results Not Yet Validated on \carmix{} (Tier 2)}

The result in this section is proven theory. The SMP foundation of the earlier
sections has narrowed its validation gap, but \carmix{} does not yet exhibit it in
running code, so it is Tier 2 and not Tier 1.

\subsection{Deterministically Reproducible Consistent Cut}

A consistent capture of a multi-core computation needs a cut of the global state
that no later replay can observe to be inconsistent. The Deterministically
Reproducible Consistent Cut, DRCC, is the formalization of that property for
content-addressed rematerialization. The result is a split along the data-race
line. For a data-race-free program, a cut taken at release-consistency
synchronization points establishes DRCC without a global stop of all cores,
because the synchronization points order the memory operations that matter and the
unsynchronized operations cannot be observed to differ. For state with a genuine
data race, DRCC is undefined, and no capture mechanism rescues it, because the
racy outcome is not a function of the cut. This is a derivation that combines the
release-consistency memory model with the consistent-cut and happened-before line
of distributed-snapshot work, applied to the content-addressed setting, rather
than a standalone discovery.

The validation gap is explicit. The SMP bring-up of the Architecture is the
foundation a multi-core capture would run on, and it now exists, so the gap has
narrowed from where it stood when only a single CPU ran. But the multi-core
consistent-capture cut is not exhibited or validated on \carmix{}. The versioned
capability gate removes the single-CPU authority transient, and the
inter-processor interrupt path is the primitive a cross-core TLB shootdown would
use, but neither is the cut. \carmix{} does not yet demonstrate multi-core
consistent capture. Doing so on the now-built SMP foundation is the first item of
future work.

\section{Research Findings and Verdicts (Tier 3)}

The findings in this section are research results whose implementation is not
built, or where only a derivation or an impossibility argument exists. A clean
negative, an impossibility or an undecidability, is itself a contribution, because
it bounds what any implementation could achieve. Each finding is labeled, and
where a finding has a built response that response is named and placed in Tier 1.

\subsection{The deduplication side-channel impossibility}

Cross-process content deduplication is a known timing and occupancy side channel.
A store that deduplicates globally answers a store of content another party holds
faster than a store of genuinely new content, which leaks the content's existence.
The formal finding, borrowed and applied from the Armknecht et al. bound, is that
zero cross-domain leakage with nonzero cross-domain sharing is impossible. Any
system that shares stored content across a trust boundary leaks across that
boundary, so the only leak-free option for the cross-domain channel is to not
share across it. This is the proven boundary. Its prescribed fix,
domain-partitioned deduplication, is built and measured and is the Tier 1 result
in the Architecture, which closes the cross-domain channel at the measured cost of
duplicate cross-domain storage, exactly the trade the bound makes unavoidable. The
copy-on-write break channel, the other classic deduplication side channel, is
structurally absent in \carmix{}, because its objects are immutable and a write
produces a new object with a new name rather than breaking a shared page.

\subsection{Content-addressed convergence}

Convergence asks whether two computations that reach the same state can be made to
share one content-addressed name for it. The verdict is split, and it is not
built. On the positive side, a computable canonical form exists for structural
equivalence of reachable state, and it preserves both determinism and
anti-amplification, provided the authority metadata is part of the hashed content
so that two states of differing authority cannot collide to one name. The
tractability of computing that canonical form is in principle only. It is
polynomial for graphs of bounded degree, by the bounded-valence graph isomorphism
result, and \carmix{}'s object arity is not measured, so the polynomial claim is
not established for \carmix{}'s graphs. On the negative side, observational or
behavioral equivalence is undecidable. Deciding whether two computations are
behaviorally equivalent reduces to the halting problem by Rice's theorem, so full
semantic convergence, sharing a name whenever two states behave the same, is
unreachable by any algorithm. The honest statement is that structural convergence
is constructible in principle with a tractability caveat, and behavioral
convergence is impossible.

\subsection{Userland phasing}

The path to a real userland is mapped as a sequence of phases, stated here as the
planned shape rather than as built work. U-0 is the smallest real userland, a
single process with an explicit bounded capability space, five gated system calls,
and an acquire-only bump allocator. U-1 follows. U-0 and U-1 are independent of the
garbage collector and the SMP work. U-2 depends on the collector and U-3 depends
on SMP, which is why those phases follow the substrates they need. At this writing
U-0 is in progress and unverified. It is not yet Tier 1, and it is not presented
as done. The currently loaded program is the static, embedded process of the
Architecture, not the U-0 userland.

\section{Limitations}

\carmix{} is roughly forty to forty-five percent of the way to a general-purpose
operating system. The following are not built, and the list is the point of this
section.

\begin{itemize}
\item \textbf{No real hardware.} Everything runs in QEMU. The bootable image runs
the same path from a USB stick, but that has not been verified on a physical
machine, and there is no real network transport, only ivshmem shared memory
between two local instances.
\item \textbf{Durable persistence is built but narrow.} A content-addressed object
and a whole dematerialized process now survive a genuine cold reboot on a
virtio-blk disk, re-verified by re-hash on every load (Tier 1). The scope is
honest and narrow. There is a single durable writer, objects are at most one
payload block, and the crash consistency is recovery-logic consistency under an
ordered-prefix write-order model in QEMU, with real-hardware write reordering,
cache and barrier semantics, and sub-sector tearing out of scope. There is still
no general filesystem or namespace, the process image is embedded in the kernel,
and the trust-store and nonce lifecycle state do not persist across a reboot.
\item \textbf{No full allocator.} A process can grow its heap through an
authority-bounded extend-heap backed demand-zero, and a userspace bump allocator
runs on the granted pages, but the bump allocator has no free, there are no huge
pages, and there is no production dedup-scan policy.
\item \textbf{No dynamic linking.} The loaded program is a static executable.
\item \textbf{Partial task-state dematerialization.} The content-addressed task
object today is the registers and the used stack only. The page-table root and the
capability slots stay resident and are not yet part of it.
\item \textbf{PM2 was serviced through the page-fault core directly.} The idle-page
rematerialization milestone calls the same C page-fault service routine the live
vector runs, rather than triggering a live fault on a freshly-unmapped low virtual
address, because a live touch there halts the boot on the single-stack handler.
The serial line says so on the wire, and the live page-fault entry is proven
separately by F1, US0, and C0.
\item \textbf{Recoverable nested faults are not supported.} A fault during fault
handling fails closed rather than recovering. Making it recoverable needs a
separate interrupt stack (IST/TSS) and a per-fault service context (F5).
\item \textbf{The fairness control rests on lighter research.} It bounds future
deficit growth and recovers the progress rate but does not refund the penalty
already paid, and it accounts for one peer rather than many. It is a first measured
control, not a proven-optimal fairness algorithm.
\item \textbf{Deduplication leakage is partly closed, not eliminated.}
Domain-partitioned deduplication closes the cross-domain store-timing channel at a
measured storage cost (Tier 1), and the cross-domain leak-freedom rests on the
proven impossibility bound (Tier 3). The within-domain timing channel remains and
is accepted, because the observer is already in that domain. The bounded-residual
mitigations, timing normalization and a randomized threshold, are not built, and a
concurrent cross-core attacker is not exercised because it depends on the SMP work.
\item \textbf{SMP is a foundation only.} A second CPU is up with per-CPU state, a
working inter-processor interrupt path, and a cross-core test that shows genuine
parallelism (Tier 1). The multi-core consistent capture and the DRCC result are
not validated on it. The DRCC result is proven theory whose validation gap has
narrowed now that the foundation exists, but \carmix{} does not yet exhibit the
multi-core cut (Tier 2).
\item \textbf{Garbage collection and convergence have limits.} The durable
collector is single-CPU. Concurrent tracing against a live multi-threaded mutator
and cross-core reclamation are not built and wait on the SMP work.
Content-addressed convergence is not built at all. Its structural canonical form is
constructible only in principle, polynomial for bounded-degree graphs while
\carmix{}'s arity is unmeasured, and its behavioral form is undecidable (Tier 3),
a hard semantic-naming boundary rather than an engineering gap.
\item \textbf{Userland is U-0 in progress, not a full userland.} The userland
phasing is a research map. U-0, the smallest real userland, is in progress and
unverified at this writing, and the later phases are planned, not built (Tier 3).
\item \textbf{The PM0 stall is a known accepted failure.} A ring-3 readback in the
per-process-memory stage stalls. It predates this work, is reported on the wire on
every run rather than hidden, and is accepted, not fixed.
\item \textbf{The trust-root bootstrap is open.} The destination's first authority
public key is baked in. How a destination obtains and proves that first key,
through a certificate authority, identity proofing, or an out-of-band channel, is
the one irreducible bootstrap assumption and is not built. There is also no
trustworthy clock for the expiry check, only a tick counter, and one authority key
whose compromise is unrecoverable.
\item \textbf{Input is polled PS/2.} Real modern hardware needs a USB HID stack
over xHCI. The desktop is software-rendered and runs no third-party graphical
applications.
\item \textbf{The proof is the abstract algebra.} It is not a refinement of the C
code. The runtime correspondence is demonstrated by the attack tables, not proven.
\end{itemize}

\section{Related Work}

\textbf{Component and safe-language operating systems.} Theseus structures the
operating system as many small interchangeable cells with state ownership tracked
by the language, to make live evolution and fault recovery
tractable~\cite{boos2020theseus}. Twizzler builds an operating system around a
single global data-centric address space over persistent
memory~\cite{bittman2020twizzler}. Hubris is a small statically-defined
memory-protected embedded operating system with no dynamic task
creation~\cite{oxide2021hubris}. Unikraft composes a specialized unikernel from
modular library components~\cite{kuenzer2021unikraft}. \carmix{} differs by making
content-addressed rematerialization, not the module, the namespace, or the
language, the unit through which it expresses context switch, fault, migration,
crossing, load, and deschedule as one operation.

\textbf{Capability and microkernel systems.} seL4 is a microkernel with a complete
machine-checked functional-correctness proof and a capability access-control
model~\cite{klein2009sel4}. EROS and its ancestor KeyKOS are
capability-based systems with transparent orthogonal persistence by periodic
checkpoint~\cite{shapiro1999eros,hardy1985keykos}. Genode is a capability-based
component framework~\cite{feske2015genode}. \carmix{} shares the capability
discipline but adds the anti-amplification re-mint as a migration and crossing
primitive, ties it to a machine-checked authority property, and unifies it with
content-addressed transfer. Its proof covers that authority algebra rather than
full kernel functional correctness.

\textbf{Migration and page deduplication.} MITOSIS migrates serverless function
state across machines efficiently~\cite{du2023mitosis}, and content-addressed or
hash-based virtual-machine and page migration has been built and measured. KSM
merges identical anonymous pages in Linux by content
scan~\cite{arcangeli2009ksm}. The nearest active project content-addresses program
binaries, naming a function by the hash of its code and sharing it across a
cluster. \carmix{} content-addresses live computation state, the running memory
graph, rather than code or post-hoc page scans, and re-mints the guarding
capabilities during the transfer, which the page-merge and binary-addressing lines
do not do.

\textbf{Content-addressed stores and hashing.} Git names objects by the SHA hash
of their content~\cite{git}, Nix builds a content-addressed package
store~\cite{dolstra2004nix}, and IPFS is a content-addressed distributed file
system~\cite{benet2014ipfs}. These address files, packages, and blocks at rest.
\carmix{} applies the same naming to live execution state and to physical-memory
residency. BLAKE3 is the hash function~\cite{blake3}, chosen for speed. The store
hashes only at commit and epoch boundaries, never in an execution loop.

\textbf{Replacement and working-set theory.} The residency manager and the
scheduling policy rest on the classical working-set model of program
locality~\cite{denning1968workingset}. \carmix{}'s contribution there is to anchor
the dematerialize decision in a measured rematerialize cost and a live break-even,
and to compose the hardware dirty bit with content-addressed dirty tracking, not a
new replacement algorithm.

\textbf{Durable content-addressed storage and reclamation.} Venti is a durable
content-addressed archival store whose blocks are named and verified by their
hash~\cite{quinlan2002venti}, and \carmix{}'s persistence substrate borrows its
self-verifying append-only model and its separation of storage from reclamation.
Reference counting and the broader reclamation literature are
standard~\cite{jones2011gchandbook}. \carmix{}'s contribution there is narrow, a
durable refcount table reconstructed across a cold reboot with a
tombstone-as-commit crash discipline, and acyclicity guaranteed by the
content-addressed naming and machine-checked rather than assumed, so no cycle
collector is needed.

\textbf{Deduplication side channels.} Cross-user deduplication leaks the existence
of content through timing and occupancy~\cite{harnik2010sidechannels}, and the
impossibility of cross-domain leak-freedom with cross-domain sharing is an
established bound~\cite{armknecht2015dedup}. \carmix{} applies that bound directly,
partitioning deduplication by authority domain to close the cross-domain channel
and paying the duplicate storage the bound makes unavoidable. The copy-on-write
break channel does not apply, because \carmix{} objects are immutable.

\textbf{Canonicalization and consistent cuts.} The convergence verdict rests on
graph canonicalization and hash-consing~\cite{filliatre2006hashconsing} and on the
bounded-valence graph isomorphism result that gives polynomial-time tractability
only for bounded degree~\cite{luks1982valence,babai2016gi}. The DRCC result rests
on the release-consistency memory model~\cite{gharachorloo1990rc}, the
data-race-free program class~\cite{adve1990wo}, the consistent-snapshot and
happened-before line~\cite{chandy1985snapshots,lamport1978clocks}, and Rice's
theorem for the undecidability of behavioral equivalence~\cite{rice1953}.
\carmix{}'s parts here are derivations and a verdict, not standalone discoveries.

The unoccupied axis is the synthesis. No prior system makes content-addressed
rematerialization under an authority-monotonic re-mint the single operation behind
context switch, fault, migration, crossing, load, and deschedule, with the
authority bound machine-checked.

\section{Conclusion and Future Work}

\carmix{} is a research operating system organized around one principle, that a
context switch, a page fault, a cross-machine migration, a user and kernel
crossing, a program load, and a process deschedule are one operation: the
rematerialization of content-addressed state under a re-minted anti-amplification
capability ceiling, over BLAKE3 hashes. The contribution is the principle and its
verified demonstration. The system boots, runs a capability-guarded WebAssembly
executor, rematerializes state on one machine and across two, persists a
content-addressed object and a whole process across a genuine cold reboot,
reclaims unreachable objects with a durable collector, partitions deduplication by
authority domain to close the cross-domain timing channel, brings up a second CPU
as a multi-core foundation, enforces one anti-amplification gate at every boundary
with the adversarial tables to show it, and machine-checks the core authority
property in Coq under one stated collision-resistance hypothesis. Those are the
Tier 1 results. It is not a finished operating system, and the Limitations section
states what is missing.

Future work follows the open items, and the Tier 2 and Tier 3 results set the
highest-value next steps. The DRCC result should be validated on the now-built SMP
foundation by exhibiting a multi-core consistent-capture cut, which is the open
multi-core question. Content-addressed convergence should be built, which is the
high-ceiling open question, bounded above by the undecidability of behavioral
equivalence. The userland phases should be completed past the in-progress U-0. The
proof should be extended to a machine-checked refinement of the C backend against
the abstract algebra, and a verified BLAKE3 should replace the vendored one once a
verified BLAKE3 is confirmed to exist. The task-state object should grow to include
the page-table root and the capability slots, recoverable nested faults need an
interrupt stack and a per-fault service context, and the scheduling policy and the
fairness control need a learned predictor and a multi-peer treatment. The platform
needs real hardware bring-up, a USB HID stack, a general filesystem and namespace
over the durable store, a full allocator, dynamic linking, and a real network
transport. The trust root needs a bootstrap for the first authority key, persistent
rollback-resistant trust and nonce state, a trustworthy clock, and revocation at
scale. Each of these is an honest open item rather than a hidden one, and the
credibility of the demonstrated parts is meant to rest on that honesty.

\begin{thebibliography}{99}

\bibitem{ritchie1974unix}
D.~M. Ritchie and K.~Thompson.
The UNIX Time-Sharing System.
\emph{Communications of the ACM}, 17(7):365--375, 1974.

\bibitem{pike1995plan9}
R.~Pike, D.~Presotto, S.~Dorward, B.~Flandrena, K.~Thompson, H.~Trickey, and
P.~Winterbottom.
Plan 9 from Bell Labs.
\emph{Computing Systems}, 8(3):221--254, 1995.

\bibitem{wahbe1993sfi}
R.~Wahbe, S.~Lucco, T.~E. Anderson, and S.~L. Graham.
Efficient Software-Based Fault Isolation.
In \emph{Proceedings of the 14th ACM Symposium on Operating Systems Principles
(SOSP)}, pages 203--216, 1993.

\bibitem{haas2017wasm}
A.~Haas, A.~Rossberg, D.~L. Schuff, B.~L. Titzer, M.~Holman, D.~Gohman,
L.~Wagner, A.~Zakai, and J.~F. Bastien.
Bringing the Web up to Speed with WebAssembly.
In \emph{Proceedings of the 38th ACM SIGPLAN Conference on Programming Language
Design and Implementation (PLDI)}, pages 185--200, 2017.

\bibitem{bernstein2012nacl}
D.~J. Bernstein, T.~Lange, and P.~Schwabe.
The Security Impact of a New Cryptographic Library.
In \emph{Progress in Cryptology -- LATINCRYPT 2012}, LNCS 7533, pages 159--176,
2012.

\bibitem{bernstein2012ed25519}
D.~J. Bernstein, N.~Duif, T.~Lange, P.~Schwabe, and B.-Y. Yang.
High-Speed High-Security Signatures.
\emph{Journal of Cryptographic Engineering}, 2(2):77--89, 2012.

\bibitem{klein2009sel4}
G.~Klein, K.~Elphinstone, G.~Heiser, J.~Andronick, D.~Cock, P.~Derrin,
D.~Elkaduwe, K.~Engelhardt, R.~Kolanski, M.~Norrish, T.~Sewell, H.~Tuch, and
S.~Winwood.
seL4: Formal Verification of an OS Kernel.
In \emph{Proceedings of the 22nd ACM Symposium on Operating Systems Principles
(SOSP)}, pages 207--220, 2009.

\bibitem{shapiro1999eros}
J.~S. Shapiro, J.~M. Smith, and D.~J. Farber.
EROS: A Fast Capability System.
In \emph{Proceedings of the 17th ACM Symposium on Operating Systems Principles
(SOSP)}, pages 170--185, 1999.

\bibitem{hardy1985keykos}
N.~Hardy.
KeyKOS Architecture.
\emph{ACM SIGOPS Operating Systems Review}, 19(4):8--25, 1985.

\bibitem{feske2015genode}
N.~Feske.
\emph{Genode Operating System Framework Foundations}.
Genode Labs, 2015.

\bibitem{boos2020theseus}
K.~Boos, N.~Liyanage, R.~Ijaz, and L.~Zhong.
Theseus: An Experiment in Operating System Structure and State Management.
In \emph{Proceedings of the 14th USENIX Symposium on Operating Systems Design and
Implementation (OSDI)}, pages 1--19, 2020.

\bibitem{bittman2020twizzler}
D.~Bittman, P.~Alvaro, P.~Mehra, D.~D.~E. Long, and E.~L. Miller.
Twizzler: A Data-Centric OS for Non-Volatile Memory.
In \emph{Proceedings of the 2020 USENIX Annual Technical Conference (ATC)},
pages 65--80, 2020.

\bibitem{oxide2021hubris}
Oxide Computer Company.
Hubris: A Memory-Protected Microcontroller Operating System.
Technical documentation, 2021.

\bibitem{kuenzer2021unikraft}
S.~Kuenzer, V.-A. B\u{a}doiu, H.~Lefeuvre, S.~Santhanam, A.~Jung, G.~Gain,
C.~Soldani, C.~Lupu, S.~Teodorescu, C.~R\u{a}ducanu, C.~Banu, L.~Mathy,
R.~Deaconescu, C.~Raiciu, and F.~Huici.
Unikraft: Fast, Specialized Unikernels the Easy Way.
In \emph{Proceedings of the 16th European Conference on Computer Systems
(EuroSys)}, pages 376--394, 2021.

\bibitem{du2023mitosis}
D.~Du, Q.~Liu, X.~Jiang, Y.~Xia, B.~Zang, and H.~Chen.
Serverless Computing on Heterogeneous Computers with Fast Function Provisioning.
\emph{(MITOSIS / serverless function migration line of work)}, 2023.

\bibitem{arcangeli2009ksm}
A.~Arcangeli, I.~Eidus, and C.~Wright.
Increasing Memory Density by Using KSM.
In \emph{Proceedings of the Linux Symposium}, pages 19--28, 2009.

\bibitem{git}
S.~Chacon and B.~Straub.
\emph{Pro Git}.
Apress, 2nd edition, 2014.

\bibitem{dolstra2004nix}
E.~Dolstra, M.~de~Jonge, and E.~Visser.
Nix: A Safe and Policy-Free System for Software Deployment.
In \emph{Proceedings of the 18th USENIX Large Installation System Administration
Conference (LISA)}, pages 79--92, 2004.

\bibitem{benet2014ipfs}
J.~Benet.
IPFS -- Content Addressed, Versioned, P2P File System.
arXiv:1407.3561, 2014.

\bibitem{blake3}
J.~O'Connor, J.-P. Aumasson, S.~Neves, and Z.~Wilcox-O'Hearn.
\emph{BLAKE3: One Function, Fast Everywhere}.
Specification, 2020.

\bibitem{denning1968workingset}
P.~J. Denning.
The Working Set Model for Program Behavior.
\emph{Communications of the ACM}, 11(5):323--333, 1968.

\bibitem{quinlan2002venti}
S.~Quinlan and S.~Dorward.
Venti: A New Approach to Archival Storage.
In \emph{Proceedings of the 1st USENIX Conference on File and Storage Technologies
(FAST)}, pages 89--101, 2002.

\bibitem{jones2011gchandbook}
R.~Jones, A.~Hosking, and E.~Moss.
\emph{The Garbage Collection Handbook: The Art of Automatic Memory Management}.
Chapman and Hall/CRC, 2011.

\bibitem{harnik2010sidechannels}
D.~Harnik, B.~Pinkas, and A.~Shulman-Peleg.
Side Channels in Cloud Services: Deduplication in Cloud Storage.
\emph{IEEE Security \& Privacy}, 8(6):40--47, 2010.

\bibitem{armknecht2015dedup}
F.~Armknecht, J.-M. Bohli, G.~O. Karame, and F.~Youssef.
Transparent Data Deduplication in the Cloud.
In \emph{Proceedings of the 22nd ACM SIGSAC Conference on Computer and
Communications Security (CCS)}, pages 886--900, 2015.

\bibitem{filliatre2006hashconsing}
J.-C. Filli\^atre and S.~Conchon.
Type-Safe Modular Hash-Consing.
In \emph{Proceedings of the 2006 ACM SIGPLAN Workshop on ML}, pages 12--19, 2006.

\bibitem{luks1982valence}
E.~M. Luks.
Isomorphism of Graphs of Bounded Valence Can Be Tested in Polynomial Time.
\emph{Journal of Computer and System Sciences}, 25(1):42--65, 1982.

\bibitem{babai2016gi}
L.~Babai.
Graph Isomorphism in Quasipolynomial Time.
In \emph{Proceedings of the 48th Annual ACM Symposium on Theory of Computing
(STOC)}, pages 684--697, 2016.

\bibitem{gharachorloo1990rc}
K.~Gharachorloo, D.~Lenoski, J.~Laudon, P.~Gibbons, A.~Gupta, and J.~Hennessy.
Memory Consistency and Event Ordering in Scalable Shared-Memory Multiprocessors.
In \emph{Proceedings of the 17th Annual International Symposium on Computer
Architecture (ISCA)}, pages 15--26, 1990.

\bibitem{adve1990wo}
S.~V. Adve and M.~D. Hill.
Weak Ordering: A New Definition.
In \emph{Proceedings of the 17th Annual International Symposium on Computer
Architecture (ISCA)}, pages 2--14, 1990.

\bibitem{chandy1985snapshots}
K.~M. Chandy and L.~Lamport.
Distributed Snapshots: Determining Global States of Distributed Systems.
\emph{ACM Transactions on Computer Systems}, 3(1):63--75, 1985.

\bibitem{lamport1978clocks}
L.~Lamport.
Time, Clocks, and the Ordering of Events in a Distributed System.
\emph{Communications of the ACM}, 21(7):558--565, 1978.

\bibitem{rice1953}
H.~G. Rice.
Classes of Recursively Enumerable Sets and Their Decision Problems.
\emph{Transactions of the American Mathematical Society}, 74(2):358--366, 1953.

\end{thebibliography}

\end{document}
